A Switching Planner for Combined Task and Observation Planning

### 2010-11-23 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
grammar
I think I have understoof Moritz's code, but I may not have...
 - Charles

\noindent A valid assumption in our setting corresponds to a {\em
relaxed} visitation of the root term of $(:init)$. In this relaxed
case, a conjunctive term is visited iff its atomic subterms are
visited, and zero or more of its immediate probabilistic subterms are
visited. The starting state, $\state_0$, for sequential planning is
the abstract state with probability $1.0$ -- E.G., for $\pp{R2D2}$
$s_0 \equiv \{(= (is-in R2D2) kitchen)\}$.

@@

\begin{equation}\label{eq:tracevalue}
V(s_0, a_0, s_1, a_1,.., s_N) =  \prod_{i=1..N} p_i \sum_{i=1..N-1} \reward(\state_i, \action_i)
\end{equation}

@@

\[
V^* = \max_{p_1, .., p_n} \prod_{i=1..N} p_i \sum_{i=1..N-1}
\reward(\state_i, \action_i),
\]

\noindent which is equal to the maximal contribution a trace of the plan can
make to Eq~\ref{eq:expectedvalue}. In other words, writing $V_i$ for
the value of the $i^{th}$ trace of the plan expressed in $s_0, a_0,
s_1, a_1,.., s_N$, we have:

\[
V^* = \arg\min_{V_i} \Expect \bigg{[} 
\sum_{t=0}^{N}  \reward(\bstate_t) \mid \pp{PLAN}, \bstate = \bstate_0
\bigg{]} - V_i
\]

In goal directed problems, where the only non-zero reward is received
at the first transition to a goal state, the Eq~\ref{eq:tracevalue}
criteria corresponds exactly to that of the infamous degenerate
hindsight system
\system{FFR$_a$}~\cite{yoon:etal:2007}. Form the perspective of
gradient-based reinforcement learning systems, such as William's
REINFORCE and GPOMDP variants for planning~\cite{olivier:doug:2009},
under reasonable assumptions the optimal trace identifies a maximal
gradient step from a uniformly random soft-max policy.

@@

>>>>

\noindent A valid assumption in our setting corresponds to a {\em
relaxed} visitation of the root term of $(:init)$. In this relaxed
case, a conjunctive term is visited iff its atomic subterms are
visited, and zero or more of its immediate probabilistic subterms are
visited. The starting state, $\state_0$, for sequential planning is
the unique abstract state with probability $1.0$ -- E.G., for
$\pp{R2D2}$ $s_0 \equiv \{(= (is-in R2D2) kitchen)\}$.

@@

\begin{equation}\label{eq:tracevalue}
V(s_0, a_0, s_1, a_1,.., s_N) =  \prod_{i=1..N-1} p_i \sum_{i=1..N-1} \reward(\state_i, \action_i)
\end{equation}

@@

\[
V^* = \max_{p_1, .., p_n} \prod_{i=1..N-1} p_i \sum_{i=1..N-1}
\reward(\state_i, \action_i),
\]

\noindent which is equal to the maximal contribution a trace of the plan can
make to Eq~\ref{eq:expectedvalue}. In other words, writing $V_i$ for
the value of the $i^{th}$ trace of the plan expressed in $s_0, a_0,
s_1, a_1,.., s_N$, we have

\[
V^* = \arg\min_{V_i} \Expect \bigg{[} 
\sum_{t=0}^{N-1}  \reward(\bstate_t, \pp{PLAN}_t) \mid \pp{PLAN}, \bstate_0
\bigg{]} - V_i.
\]

In goal directed problems, where the only non-zero reward is received
at the first transition to a goal state, the Eq~\ref{eq:tracevalue}
criteria corresponds exactly to that of the infamous degenerate
hindsight system
\system{FFR$_a$}~\cite{yoon:etal:2007}. Form the perspective of
gradient-based reinforcement learning systems, such as William's
REINFORCE and GPOMDP variants for planning~\cite{olivier:doug:2009},
under reasonable assumptions the optimal trace identifies a maximal
gradient step from a uniformly random soft-max policy. Finally, it is
worth clarifying that although the above discussion has been in terms
of a trace of length $N$, there is nothing in our approach that
artificially limits the length of candidate sequential plans.

@@

In the decision-theoretic mode, the switching planner solves a sensing
problem in an abstract processes defined in terms of the assumptive
actions in the current sequential plan. Therefore, this mode uses a
different utility model, that reflects the value of performing sensing
actions.

We construct a {\em relaxed} $(\pp{:init})$ block by first
constructing a tree which only includes terms from the {\em relaxed}
visitation characterised by the {\em assumptive} actions in the
current sequential plan. For example, if $\pp{R2D2}$'s plan is:

\[
\begin{array}{c}
\actions(.8,(=(\pp{is-in}~\pp{box})\pp{office}));\\
(pp{reportlook-for-object}~\pp{R2D2}~\pp{box}~\pp{office});\\
(\pp{report-is-in}~\pp{box}~\pp{office})
\end{array}
\]

\noindent Then the {\em relaxed} block will be,

\small
\begin{tabtt}
(\=:init (= (is-in R2D2) kitchen) \+ \\
       (probabilistic \=.8 (= (is-in box) office)  \\
		      \>.2 (= (is-in box) kitchen))) \\
\end{tabtt}
\normalsize

\noindent and therefore, the belief-state $\bstate_0$ is:

\small
\begin{tabular}{cccc}
\hline
Probability & (is-in R2D2)  & (is-in box)  & (is-in cup) \\
\hline
.8 & kitchen & office & \# \\
.2 & kitchen & kitchen & \# \\
\hline
\end{tabular}
\normalsize

\noindent At this point, decision-theoretic planning would proceed in a cupless
abstraction of the environment, where the inclusion (exclusion) of
POMDP actions is the same as we defined it for the sequential mode.

In the second step, we iteratively add terms from the original
$(\pp{:init})$ block while the resulting state space remains of a
practicable size. Of course, it is expensive to measure size exactly,
thus in practice we estimate it to be $2^{|\propositions^\#|}$, where
$\propositions^\#$ is the set of propositions in the abstraction
induced by the proposed tree. Terms are proposed for addition, because
they are probabilistic, and because they were omitted in the {\em
relaxed} visitation characterised by {\em assumptive} actions in the
sequential plan. Each iteration, we add one candidate term with the
largest number of parent terms.

Terms a proposed sequentially, with preference given to
terms that are closest to, or which otherwise are, the conjunctive
leaves.
